First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-05-13 eg6-letters/coherent/dvcs_he4_prl.tex
Remarks from EV, MG and MD added.

%
\date{\today}
\begin{abstract}
We report on the first measurement of the beam-spin asymmetry in the exclusive 
process of coherent deeply virtual Compton scattering off a nucleus. The 
experiment used the 6 GeV electron beam from the CEBAF accelerator at Jefferson 
Lab incident on a $^4$He gas target in front of the CEBAF large acceptance 
spectrometer (CLAS). The scattered electron was detected by CLAS and the gamma 
by a dedicated electromagnetic calorimeter at forward angles. To ensure the 
exclusivity of the process, a specially designed radial time projection chamber 
was used to detect the recoiling $^4$He nuclei. We measured beam-spin 
asymmetries larger than those observed on the free proton in the same kinematic 
domain. From these, we were able to extract, in a model-independent way, the 
real and imaginary parts of the $^4$He unique Compton form factor, $\cal H_A$. 
This pioneering measurement of coherent deeply virtual Compton scattering on 
the $^4$He nucleus, with a fully exclusive final state via nuclear recoil 
tagging, leads the way toward 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

The generalized parton distribution (GPD) framework offers the opportunity to 
obtain information about the momentum and spatial degrees of freedom of the 
quarks and gluons inside hadrons \cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,
Radyushkin:1996nd,Radyushkin:1997ki}. In impact parameter space the GPDs are 
indeed interpreted as a tomography of the transverse plane for partons 
carrying a given fraction of the proton longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}. The most 
promising way to access GPDs experimentally is through the measurement of 
deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
electroproduction of a real photon on a hadron. While other processes are known 
to be sensitive to GPDs, the measurement of DVCS is considered the cleanest 
probe and has been the focus of efforts at Jefferson Lab, HERA, and CERN 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,
MunozCamacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,
Pisano:2015,Jo:2015ema,Joerg:2016hhs}. The vast majority of these measurements 
focused on the study of the proton and allowed for an extraction of its 
three-dimensional image (for reviews of the field, see~\cite{Goeke:2001tz,
Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}). This 
recent progress could also be applicable to nuclei, giving access to novel 
information about nuclear structure in terms of quarks and gluons 
(see~\cite{Dupre:2015jha} and references therein). Such a study of the 3D 
structure of nuclei appears to be especially interesting in light of the large, 
yet unresolved, nuclear effects observed in nuclear parton distribution 
functions~\cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}. The results 
presented in this letter demonstrate the feasability of such an approach and 
constitute a first step toward a tomography of nuclei.

@@

\begin{align}
\begin{split}
\Re e(&\mathcal{H}_{A}) = \\
    &\mathcal{P} 
\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
\end{split} \\
\Im m(&\mathcal{H}_{A}) = H_A(\xi,\xi,t)-H_A(-\xi,\xi,t),
\end{align}
with $H_A$ the GPDs, $\mathcal{P}$ 
the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).

Until now, the only available data on nuclear DVCS was from the HERMES 
experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based 
only on kinematic cuts on the measured scattered electron and real photon. The 
measurement was performed on a large set of nuclei ($^4$He, $^{14}$N, $^{20}$Ne, $^{85}$Kr and $^{131}$Xe), 
but contamination from incoherent processes could influence the measurement 
significantly~\cite{Guzey:2003jh}. The direct detection of the recoil nucleus 
can however guarantee that the nucleus remains intact.

@@

In our kinematics, the recoil $^4$He nuclei produced in DVCS have low momentum,
averaging 300 MeV. CLAS could not detect such low-energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light radial time projection chamber (RTPC) to complement CLAS. The 
RTPC was a $20$-cm-long cylinder with a diameter of $15$ cm, positioned in the 
solenoid magnet. In the center of the RTPC was the target, a $25$-cm-long 
and $6$-mm-diameter Kapton tube with $27$-$\mu$m-thick walls filled with 
6~atm of gaseous $^4$He. The experiment (E08-024) collected
data over 40 days at the end of 2009 using a 
nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
polarization) at an energy of 6.064 GeV. The RTPC was calibrated specifically 
for the detection of $^4$He nuclei using elastic scattering 
($e^4$He$\to e^\prime$$^4$He) with a 1.2~GeV electron beam.

%DVCS selection
To identify coherent DVCS events, we first selected events where one electron, 
one $^4$He, and at least one photon were detected in the final state. Electrons 
were identified using their measured momentum, light yield, time, and energy obtained from 
the CLAS drift chambers, \^{C}erenkov counters, scintillator counters, 
and electromagnetic calorimeters, respectively. The recoiling $^4$He nuclei 
were identified in the RTPC using time and energy-loss cuts for tracks in the 
fiducial region~\cite{Hattawy:thesis}. In addition, we applied a vertex-matching 
cut to ensure that the 
electron and helium nucleus originated from a common reaction vertex in the 
target cell. The photons were 
detected in either the IC or the CLAS electromagnetic calorimeters. Note that 
even though the DVCS reaction has only one real photon in the final state, 
events with more than one good photon were not discarded at this stage. These
were caused by accidental coincidences of soft photons and did not affect 
directly our measurement. We consider only the most energetic photon of an 
event as a DVCS photon candidate.
This prescription however slightly increased the corrections associated with
the $\pi^0$ and the accidental backgrounds discussed below.

@@

\begin{figure}[tb]
\includegraphics[width=9cm]{figs/F_all_coh_exc_cuts-pub.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the initial candidate events, while the shaded 
distributions represent those that passed all of the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied cuts.
The distributions from left to right and from top to bottom are: coplanarity 
angle $\Delta \phi$, missing energy $E_X$, missing-mass-squared $M_X^2$, and 
the cone angle $\theta$ between the measured photon and the missing momentum 
of the $e^\prime{^4}$He$^\prime$ system.}
\label{fig:kin-cuts}
\end{figure}

@@

We identified two main backgrounds to our measurement, accidental coincidences 
and exclusive coherent
$\pi^0$ production. The accidentals have particles originating from different events,
and we estimated their contribution to be 4.1\% of our sample. We evaluated this 
contribution by selecting events passing all our cuts but with the scattered electron and 
$^4$He originating from different vertices. The $\pi^0$ production can easily
be mistaken for DVCS when one of the two photons from the $\pi^0$ 
decay is produced at low energy in the laboratory frame and remains undetected.  
To estimate the effect of this contamination, we developed an event generator 
tuned on the experimental yield of exclusive $\pi^0$ with two photons measured. 
We used this generator together with a GEANT3 simulation of our 
detectors to estimate the ratio of the number of $\pi^0$ events where the 
two photons are detected to those that are misidentified as DVCS events. This 
ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
correct the DVCS data. Depending on the kinematics, we found contaminations of 
2 to 4\%.

%asymmetries
In this work, the physics observable extracted using coherent DVCS events is
the beam-spin asymmetry, noted $A_{LU}$. On an unpolarized target, $A_{LU}$ is 
defined as the difference of cross sections for the reaction with opposite beam 
helicities normalized to the total cross section:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+(-)}$ is the DVCS differential cross 
section for positive (negative) beam helicity. 
In this ratio, luminosity normalization and
detector efficiencies largely cancel and $A_{LU}$ can be 
extracted from the reaction yields for the two helicities ($N^{+/-}$)
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
\end{equation}
where $P_{B}$ is the degree of longitudinal polarization of the incident electron beam.

There is an additional process contributing to the same final state as the 
DVCS, the so called Bethe-Heitler (BH) process, where the real photon is 
emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
indistinguishable experimentally and the amplitude of electroproduction of real
photons includes a sum of the amplitudes of these two processes. The BH 
amplitude depends of the target form factors, while the DVCS amplitude 
depends on GPDs. For our kinematics, the cross section of real photon 
electroproduction is dominated by the BH contribution, while the DVCS 
contribution is very small. However, the DVCS contribution is
enhanced in the observables sensitive to the interference term, {\it e.g.} 
$A_{LU}$. The three terms entering the cross section calculation,
the square of the BH and DVCS amplitudes and their interference term, depend on the
azimuthal angle $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes,
as shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the $A_{LU}$ 
of a spin-zero hadron can be expressed as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
explicit expressions of the kinematic factors $\alpha_i$ are written in
Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
azimuthal angle $\phi$, the nuclear form factor $F_A(t)$, $Q^2$, $x_B$,
$x_{A} = \frac{x_{B}M_{N}}{M_{A}}$, $y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, and 
$\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$, where $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
both the imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
by fitting the $A_{LU}(\phi)$ distribution.

We present in Fig.~\ref{fig:alu} $A_{LU}$ as a function of azimuthal angle 
$\phi$ and the kinematical variables $Q^2$, $x_B$, and $t$. Due to our limited 
statistics, the latter are studied separately with independent binning. The curves on 
the plots are fits using the function presented in Eq.~(\ref{eq:A_LU-coh}), 
where the real and imaginary parts of the CFF $\mathcal{H}_{A}$ are the only 
free parameters.

\begin{figure}[tb]
\includegraphics[width=9cm]{figs/F_Coherent_ALU_phi.pdf}
\caption{The coherent $A_{LU}$ as a function of azimuthal angle $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and $t$ 
   bins (bottom panel).  The error bars represent the statistical 
   uncertainties. The grey bands represent the systematic uncertainties, 
   including the normalisation uncertainties. The red curves are the results of 
our fits with the form of equation Eq.~(\ref{eq:A_LU-coh}).}
\label{fig:alu}
\end{figure}

Studies of systematic uncertainties showed that the main contributions 
come from the choice of DVCS exclusivity cuts (8\% systematic uncertainty) and the 
large binning size (5.1\%). The values are relative and quoted for $A_{LU}$
at $\phi=90^\circ$. Added quadratically, the total systematic uncertainty
is about 10\% at $90^\circ$ (or 0.03, in absolute), which is significantly smaller
than the statistical uncertainties in all kinematical bins.

In Fig.~\ref{fig:alu90}, the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
are compared to theoretical calculations by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. The model accounts for the effect of the nucleon virtuality 
(off-shellness) on the quark distribution. The calculations are at slightly 
different kinematics than our data but still allow drawing some conclusions. The 
calculations appear to have smaller asymmetries than observed. 
The difference may arise from the theoretical uncertainty in the determination 
of the crossing point where the parton nuclear distribution becomes larger than the 
nucleon one, and reverses the sign of the nuclear effect.

\begin{figure*}[tb]
\includegraphics[width=16cm]{figs/F_Coherent_ALU_phi_90.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
   $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (a positron beam was used) inclusive measurements 
   \cite{Airapetian}, and the curves represent the theoretical calculations 
   from \cite{simonetta_2}.}
\label{fig:alu90}
\end{figure*}

@@

The results in Fig.~\ref{fig:CFF_HA} show that the extraction of the CFF
from the $A_{LU}$ is possible without model-dependent assumptions beyond
leading-twist and leading-order dominance. The amplitude and the dependencies 
observed as a function of 
$Q^{2}$, $x_B$, and $t$ are in agreement with the theoretical expectations. One 
can see a difference between the precision of the extracted imaginary and real 
parts, which is expected because of Eq.~(\ref{eq:A_LU-coh}) where 
$\alpha_2$ is much smaller than $\alpha_1$. While the precision of this 
measurement is not at a sufficient level to discriminate between the models, 
these results demonstrate the possibility of extracting the CFF of a spin-0 
target directly from a $A_{LU}$ measurement.

@@

\bibitem{Stepanyan:2001sm}
%S.~Stepanyan {\it et al.} [CLAS Collaboration],
S.~Stepanyan {\it et al.},
Phys.\ Rev.\ Lett. {\bf 87}, 182002 (2001).

\bibitem{Airapetian}
%A. Airapetian {\it et al.} [HERMES Collaboration],
A. Airapetian {\it et al.},
Phys.\ Rev.\ Lett. {\bf 87}, 182001 (2001);
JHEP {\bf 1207}, 032 (2012);
JHEP {\bf 1006}, 019 (2010);
JHEP {\bf 0806}, 066 (2008);
Phys.\ Lett.\ B {\bf 704}, 15 (2011);
Phys.\ Rev.\  D {\bf 75}, 011103 (2007);
JHEP {\bf 0911}, 083 (2009);
Phys.\ Rev.\ C {\bf 81}, 035202 (2010);
JHEP {\bf 1210}, 042 (2012).

\bibitem{Chekanov:2003ya}
%S. Chekanov {\it et al.} [ZEUS Collaboration],
S. Chekanov {\it et al.},
Phys.\ Lett.\  B {\bf 573}, 46 (2003).

\bibitem{Aktas:2005ty}
%A. Aktas {\it et al.} [H1 Collaboration],
A. Aktas {\it et al.},
Eur.\ Phys.\ J.\ C {\bf 44}, 1 (2005).

\bibitem{Chen:2006na} 
%S.~Chen {\it et al.} [CLAS Collaboration],
S.~Chen {\it et al.},
Phys.\ Rev.\ Lett.\ {\bf 97}, 072002 (2006).

\bibitem{MunozCamacho:2006hx} 
%C. Mu\~noz Camacho {\it et al.} [Jefferson Lab Hall A Collaboration],
C. Mu\~noz Camacho {\it et al.},
Phys.\ Rev.\ Lett. {\bf 97}, 262002 (2006).

\bibitem{Girod:2007aa} 
%F.X. Girod {\it et al.} [CLAS Collaboration],
F.X. Girod {\it et al.},
Phys.\ Rev.\ Lett. {\bf 100}, 162002 (2008).

\bibitem{Mazouz:2007aa} 
%   M.~Mazouz {\it et al.} [Jefferson Lab Hall A Collaboration],
   M.~Mazouz {\it et al.},
   Phys.\ Rev.\ Lett.\  {\bf 99}, 242501 (2007)

\bibitem{Gavalian:2009} 
%G. Gavalian {\it et al.} [CLAS Collaboration],
G. Gavalian {\it et al.},
Phys.\ Rev.\ C {\bf 80}, 035206 (2009).

\bibitem{Seder:2015} 
%E. Seder {\it et al.} [CLAS Collaboration],
E. Seder {\it et al.},
Phys.\ Rev.\ Lett. {\bf 114}, 032001 (2015).

\bibitem{Pisano:2015} 
%S.~Pisano {\it et al.} [CLAS Collaboration],
S.~Pisano {\it et al.},
Phys.\ Rev.\ D {\bf 91}, 052014 (2015).

>>>>

%
\date{\today}
\begin{abstract}
We report on the first measurement of the beam-spin asymmetry in the exclusive 
process of coherent deeply virtual Compton scattering off a nucleus. The 
experiment used the 6 GeV electron beam from the CEBAF accelerator at Jefferson 
Lab incident on a pressured $^4$He gaseous target in front of the CEBAF large acceptance 
spectrometer (CLAS). The scattered electron was detected by CLAS and the photon 
by a dedicated electromagnetic calorimeter at forward angles. To ensure the 
exclusivity of the process, a specially designed radial time projection chamber 
was used to detect the recoiling $^4$He nuclei. We measured beam-spin 
asymmetries larger than those observed on the free proton in the same kinematic 
domain. From these, we were able to extract, in a model-independent way, the 
real and imaginary parts of the $^4$He only Compton form factor, $\cal H_A$. 
This pioneering measurement of coherent deeply virtual Compton scattering on 
the $^4$He nucleus, with a fully exclusive final state via nuclear recoil 
tagging, leads the way toward 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

The generalized parton distribution (GPD) framework offers the opportunity to 
obtain information about the momentum and spatial degrees of freedom of the 
quarks and gluons inside hadrons \cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,
Radyushkin:1996nd,Radyushkin:1997ki}. In impact parameter space the GPDs are 
indeed interpreted as a tomography of the transverse plane for partons 
carrying a given fraction of the proton longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}. The most 
promising way to access GPDs experimentally is through the measurement of 
deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
electroproduction of a real photon on a hadron. While other processes are known 
to be sensitive to GPDs, the measurement of DVCS is considered the cleanest 
probe and has been the focus of efforts at Jefferson Lab, HERA, and CERN 
\cite{Stepanyan:2001sm,Airapetian,Airapetian:2010nu,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,
MunozCamacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Defurne:2015kxq,
Pisano:2015,Jo:2015ema,Joerg:2016hhs}. The vast majority of these measurements 
focused on the study of the proton and allowed for an extraction of its 
three-dimensional image (for reviews of the field, see~\cite{Goeke:2001tz,
Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}). This 
recent progress could also be applicable to nuclei, giving access to novel 
information about nuclear structure in terms of quarks and gluons 
(see~\cite{Dupre:2015jha} and references therein). Such a study of the 3D 
structure of nuclei appears to be especially interesting in light of the large, 
yet unresolved, nuclear effects observed in nuclear parton distribution 
functions~\cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}. The results 
presented in this letter demonstrate the feasability of such an approach and 
constitute the first step toward a tomography of nuclei.

@@

\begin{align}
\begin{split}
\Re e(&\mathcal{H}_{A}) = \\
    &\mathcal{P} 
\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
\end{split} \\
\Im m(&\mathcal{H}_{A}) = H_A(\xi,\xi,t)-H_A(-\xi,\xi,t),
\end{align}
with $H_A$ a GPD, $\mathcal{P}$ 
the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).

Until now, the only available data on nuclear DVCS was from the HERMES 
experiment \cite{Airapetian:2010nu}. In this experiment, the exclusivity of 
the reaction was obtained through kinematic cuts using only the measured 
scattered electron and real photon. The measurement was performed on a large 
set of nuclei ($^4$He, $^{14}$N, $^{20}$Ne, $^{85}$Kr and $^{131}$Xe), 
but contamination from incoherent processes could influence the measurement 
significantly~\cite{Guzey:2003jh}. The direct detection of the recoil nucleus 
can however guarantee that the nucleus remains intact.

@@

In the kinematic range of the present experiment, the recoil $^4$He nuclei 
have low momentum, averaging 300 MeV. CLAS could not detect such low-energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light radial time projection chamber (RTPC). The 
RTPC was a $20$-cm-long cylinder with a diameter of $15$ cm, positioned in the 
solenoid magnet. In the center of the RTPC was the target, a $25$-cm-long 
and $6$-mm-diameter Kapton tube with $27$-$\mu$m-thick walls filled with 
gaseous $^4$He at 6~atm. The experiment (E08-024)~\cite{Hafidi:2008pr} collected
data over 40 days at the end of 2009 using a 
nearly 100\% duty factor, longitudinally polarized electron beam (83.7$\pm 3.5 \%$ 
polarization~\cite{Perrin:thesis}) at an energy of 6.064 GeV. The RTPC was calibrated specifically 
for the detection of $^4$He nuclei using elastic scattering 
($e^4$He$\to e^\prime$$^4$He) with a 1.2~GeV electron beam.

%DVCS selection
To identify coherent DVCS events, we first selected events where one electron, 
one $^4$He, and at least one photon were detected in the final state. Electrons 
were identified using their measured momentum, light yield, time, and energy obtained from 
the CLAS drift chambers, \v{C}erenkov counters, scintillator counters, 
and electromagnetic calorimeters, respectively. The recoiling $^4$He nuclei 
were identified in the RTPC using time and energy-loss cuts for tracks in the 
fiducial region~\cite{Hattawy:thesis}. In addition, we applied a vertex-matching 
cut to ensure that the 
electron and helium nucleus originated from a common reaction vertex in the 
target cell. The photons were 
detected in either the IC or the CLAS electromagnetic calorimeters. Note that 
even though the DVCS reaction has only one real photon in the final state, 
events with more than one good photon were not discarded at this stage. These
were caused by accidental coincidences of soft photons and did not affect 
directly the measurement as only the most energetic photon of an 
event was considered a DVCS photon candidate.
This prescription however slightly increased the corrections associated with
the $\pi^0$ and the accidental backgrounds discussed below.

@@

\begin{figure}[tb]
\centering
\hspace{-0.45cm}
\includegraphics[width=9cm]{figs/F_all_coh_exc_cuts-pub.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the initial candidate events, while the shaded 
distributions represent those that passed all of the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied cuts.
The distributions from left to right and from top to bottom are: coplanarity 
angle $\Delta \phi$, missing energy $E_X$, missing-mass-squared $M_X^2$, and 
the cone angle $\theta$ between the measured photon and the missing momentum 
of the $e^\prime{^4}$He$^\prime$ system.}
\label{fig:kin-cuts}
\end{figure}

@@

We identified two main backgrounds, accidental coincidences and exclusive coherent
$\pi^0$ production. The accidentals have particles originating from different events,
and we estimated their contribution to be 4.1\% of our sample. We evaluated this 
contribution by selecting events passing all the cuts but with the scattered electron and 
$^4$He originating from different vertices. The $\pi^0$ production can easily
be mistaken for DVCS when one of the two photons from the $\pi^0$ 
decay is produced at low energy in the laboratory frame and remains undetected.  
To estimate the effect of this contamination, we developed an event generator 
tuned on the experimental yield of exclusive $\pi^0$ with two photons measured. 
We used this generator together with a GEANT3 simulation of our 
detectors to estimate the ratio of the number of $\pi^0$ events where the 
two photons are detected to those that are misidentified as DVCS events. This 
ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
correct the DVCS data. Depending on the kinematics, we found contaminations of 
2 to 4\%.

%asymmetries
In this work, the physics observable extracted using coherent DVCS events is
the beam-spin asymmetry, noted $A_{LU}$. On an unpolarized target, $A_{LU}$ is 
defined as the difference of cross sections for the reaction with opposite beam 
helicities normalized to the total cross section:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{\pm}$ is the DVCS differential cross 
section for positive (negative) beam helicity. 
In this ratio, luminosity normalization and
detector efficiencies largely cancel and $A_{LU}$ can be 
extracted from the reaction yields for the two helicities ($N^{\pm}$)
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
\end{equation}
where $P_{B}$ is the degree of longitudinal polarization of the incident electron beam.

There is an additional process contributing to the same final state as the 
DVCS, the so called Bethe-Heitler (BH) process, where the real photon is 
emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
indistinguishable experimentally and the amplitude of electroproduction of real
photons includes a sum of the amplitudes of these two processes. The BH 
amplitude depends on the target form factors, which are well known in this
kinematic region, while the DVCS amplitude depends on the GPDs we are trying to
measure. For our kinematics, the cross section of real photon 
electroproduction is dominated by the BH contribution, while the DVCS 
contribution is very small. However, the DVCS contribution is
enhanced in the observables sensitive to the interference term, {\it e.g.} 
$A_{LU}$. The three terms entering the cross section calculation,
the square of the BH and DVCS amplitudes and their interference term, depend on the
azimuthal angle $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes,
as shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the $A_{LU}$ 
of a spin-zero hadron can be expressed as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
explicit expressions of the kinematic factors $\alpha_i$ are derived in
Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
azimuthal angle $\phi$, the nuclear form factor $F_A(t)$ and kinematical
factors. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
both the imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
by fitting the $A_{LU}(\phi)$ distribution.

We present in Fig.~\ref{fig:alu} $A_{LU}$ as a function of azimuthal angle 
$\phi$ and the kinematical variables $Q^2$, $x_B$, and $t$. Due to limited 
statistics, these latter variables are studied separately with independent 
binning. The curves on 
the plots are fits using the function presented in Eq.~(\ref{eq:A_LU-coh}), 
where the real and imaginary parts of the CFF $\mathcal{H}_{A}$ are the only 
free parameters.

\begin{figure}[tb]
   \centering
\includegraphics[width=8.5cm]{figs/F_Coherent_ALU_phi.pdf}
\caption{$A_{LU}$ as a function of azimuthal angle $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and $t$ 
   bins (bottom panel).  The error bars represent the statistical 
   uncertainties. The grey bands represent the systematic uncertainties, 
   including the normalisation uncertainties. The red curves are the results of 
   fits with Eq.~(\ref{eq:A_LU-coh}).}
\label{fig:alu}
\end{figure}

Studies of systematic uncertainties showed that the main contributions 
come from the choice of DVCS exclusivity cuts (8\% systematic uncertainty) and the 
large binning size (5.1\%). The values are relative and quoted for $A_{LU}$
at $\phi=90^\circ$. Added quadratically, the total systematic uncertainty
is about 10\% at $90^\circ$ (or 0.03, in absolute), which is significantly smaller
than the statistical uncertainties at all kinematical bins.

In Fig.~\ref{fig:alu90}, the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The comparison to HERMES data
shows that we obtain the same sign, but the size of the error bars and the difference
of kinematics do not permit to say much more. The $x_{B}$ and $t$-dependencies 
are also compared to theoretical calculations by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. The model accounts for the effect of the nucleon virtuality 
(off-shellness) on the quark distribution. The calculations are at slightly 
different kinematics than our data but still allow drawing some conclusions. The 
calculations appear to have smaller asymmetries than observed. 
The difference may arise from the theoretical uncertainty in the determination 
of the crossing point where the parton nuclear distribution becomes larger than the 
nucleon one, and reverses the sign of the nuclear effect.

\begin{figure*}[tb]
\includegraphics[width=16cm]{figs/F_Coherent_ALU_phi_90.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
   $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (a positron beam was used) inclusive measurements 
   \cite{Airapetian}, and the curves are the theoretical calculations 
   from \cite{simonetta_2}. The grey bands represent the systematic errors.}
\label{fig:alu90}
\end{figure*}

@@

The results in Fig.~\ref{fig:CFF_HA} show that the extraction of the CFF
from the $A_{LU}$ is possible without model-dependent assumptions beyond
leading-twist and leading-order dominance. The amplitude and the dependencies 
observed as a function of 
$Q^{2}$, $x_B$, and $t$ are in agreement with the theoretical expectations. One 
can see a difference between the precision of the extracted imaginary and real 
parts, which is built in Eq.~(\ref{eq:A_LU-coh}) where 
$\alpha_2$ is much smaller than $\alpha_1$. While the precision of this 
measurement is not at a sufficient level to discriminate between the models, 
these results demonstrate the possibility of extracting the CFF of a spin-0 
target directly from a $A_{LU}$ measurement.

@@

\bibitem{Stepanyan:2001sm}
S.~Stepanyan {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ Lett. {\bf 87}, 182002 (2001).

\bibitem{Airapetian}
A. Airapetian {\it et al.} [HERMES Collaboration],
Phys.\ Rev.\ Lett. {\bf 87}, 182001 (2001);
Phys.\ Rev.\  D {\bf 75}, 011103 (2007);
JHEP {\bf 0806}, 066 (2008);
JHEP {\bf 0911}, 083 (2009);
JHEP {\bf 1006}, 019 (2010);
Phys.\ Lett.\ B {\bf 704}, 15 (2011);
JHEP {\bf 1207}, 032 (2012);
JHEP {\bf 1210}, 042 (2012).

\bibitem{Airapetian:2010nu}
A. Airapetian {\it et al.} [HERMES Collaboration],
Phys.\ Rev.\ C {\bf 81}, 035202 (2010).

\bibitem{Chekanov:2003ya}
S. Chekanov {\it et al.} [ZEUS Collaboration],
Phys.\ Lett.\  B {\bf 573}, 46 (2003).

\bibitem{Aktas:2005ty}
A. Aktas {\it et al.} [H1 Collaboration],
Eur.\ Phys.\ J.\ C {\bf 44}, 1 (2005).

\bibitem{Chen:2006na} 
S.~Chen {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ Lett.\ {\bf 97}, 072002 (2006).

\bibitem{MunozCamacho:2006hx} 
C. Mu\~noz Camacho {\it et al.} [Jefferson Lab Hall A Collaboration],
Phys.\ Rev.\ Lett. {\bf 97}, 262002 (2006).

\bibitem{Girod:2007aa} 
F.X. Girod {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ Lett. {\bf 100}, 162002 (2008).

\bibitem{Mazouz:2007aa} 
   M.~Mazouz {\it et al.} [Jefferson Lab Hall A Collaboration],
   Phys.\ Rev.\ Lett.\  {\bf 99}, 242501 (2007)

\bibitem{Gavalian:2009} 
G. Gavalian {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ C {\bf 80}, 035206 (2009).

\bibitem{Seder:2015} 
E. Seder {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ Lett. {\bf 114}, 032001 (2015).

\bibitem{Defurne:2015kxq} 
  M.~Defurne {\it et al.} [Jefferson Lab Hall A Collaboration],
  Phys.\ Rev.\ C {\bf 92}, no. 5, 055202 (2015).

\bibitem{Pisano:2015} 
S.~Pisano {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ D {\bf 91}, 052014 (2015).

\bibitem{Jo:2015ema}
H.~S.~Jo {\it et al.} [CLAS Collaboration],
  Phys.\ Rev.\ Lett.\  {\bf 115}, no. 21, 212003 (2015)
